Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-02 paper.tex
Write more on preliminaries

\title{Test Title}

@@

Let $H\in\mathbb{R}^{N\times N}$ be Hermitian.

@@

Given $H_1, \ldots, H_n\in\mathbb{R}^{N\times N}$, where each $H_j$ is Hermitian and has nonzero entries on at most $c\in\mathbb{N}$ rows and columns.
Given $a<b$ with some inverse polynomial gap, let $H=\sum H_j$, decide whether $\lambda(H)<a$ or $\lambda(H)>b$..

\begin{theorem}
	Local Hamiltonian is QMA-complete.
\end{theorem}

@@

First, we apply the transform given in \cite{1109.0795} to the desired quantum circuit. Everything is real numbers from here on. Note that this preserves the results of X/Z measurements. Then, we transform the circuit following the projection lemma construction described in \cite{quant-ph/0406180}. Additionally, we also double the size of the circuit by padding identity matrices at the end. We then follow the rest of \cite{quant-ph/0406180} and reduce the circuit into a 2-Local Hamiltonian instance. We can then turn all the Hamiltonians involved into some combinations of $X$ and $Z$ matrices following \cite{0704.1287}.

@@

\section{Stuff}

>>>>

\title{Placeholder Title... Something About Delegating Quantum Computations}

@@

Let $\mathcal{B}$ denote the Hilbert space corresponding to a qubit.
Let $H:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian.

\begin{definition}
	Let $H\geq0$ denote $H$ is positive semidefinite.
\end{definition}

@@

\begin{definition}
	Let $H_1, \ldots, H_n:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian. Then $$H=\sum_{j=1}^nH_j$$ is called a \emph{Hamiltonian}.
	If each $H_j$ acts on at most $k$ qubits, then $H$ is called a \emph{$k$-local Hamiltonian}.
\end{definition}

The local Hamiltonian problem is given by let $a<b$ with some inverse polynomial gap, let $H=\sum H_j$, determine whether $\lambda(H)<a$ or $\lambda(H)>b$..

\begin{theorem}
	The Local Hamiltonian problem is QMA-complete.
\end{theorem}

\subsection{Projection Lemma}

Here is a lemma that we will use, taken from \cite{quant-ph/0406180}.

Let $H_1, H_2$ be Hamiltonians where $H_2\geq0$, and $S=\ker H_2$.
Then $\exists J\in\mathbb{R}$ s.t.
$\lambda(H_1\big|_S)-\frac{1}{8}\leq
	\lambda(H_1+JH_2)\leq\lambda(H_1\big|_S)$.

@@

\subsection{Preprocessing the circuit}

We first take our universal

\subsection{Reduction to Real Quantum Computation}

The transform is found in \cite{1109.0795}. It turns the states and the unitary matrices into real numbers.

Then, we transform the circuit following the projection lemma construction described in \cite{quant-ph/0406180}. Additionally, we also double the size of the circuit by padding identity matrices at the end. We then follow the rest of \cite{quant-ph/0406180} and reduce the circuit into a 2-Local Hamiltonian instance. We can then turn all the Hamiltonians involved into some combinations of $X$ and $Z$ matrices following \cite{0704.1287}.

Note that this preserves the results of X/Z measurements.

\subsection{Reduction to 2-local Hamiltonians}

@@

\subsection{Test computation}

\subsection{Stuff}
